---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 15"
author: Xiaoying Wang
output: html_notebook
---

## Assigned Exercises

- DC Chapter 15 Exercises: 15.1, 15.3, 15.5


## Front Matter

```{r}

# all packages used for the assignment
library(dcData)
library(tidyverse)
library(mosaic)
library(ggplot2)
mosaicData::CPS85
```

### Problem 15.1
```{r}
CPS85 %>%
  ggplot(aes(x = sex, y = wage, fill = sex)) +
  geom_boxplot() +
  theme_bw()

```

### Problem 15.3

```{r}
CPS85 %>%
  ggplot(aes(x = educ, y = wage, color = sex)) +
  geom_point() +
  stat_smooth(method = lm) +
  ylim(0,15)+

  theme_bw()

```

### Problem 15.5
1. 
No, from the graph, we can see that the line is slope downward. In contrast, high elderly populations tend to have low child populations.

2. 
Yes, Since the regression line downward and not parallel, we can see that there is a inverse relationship between elderly population and child population. As a result, there is a relationship between elderly population and child population.

1. 
No, it is not consistent with data since two graph have different slope. The second graph have 80 data points as compared to 20 data points, so it is not consistent with the data. Larger sample size will have larger confidence interval. 

2.
Roughly the ratio of confidence band heights is 2:1

3. Yes, it is right.

