---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 12"
author: Xiaoying Wang
output: html_notebook
---

## Assigned Exercises

- DC Chapter 12 Exercises: 12.2, 12.3


## Front Matter

```{r}

# all packages used for the assignment
library(dcData)
library(tidyverse)
library(mosaic)
library(ggplot2)
```

### Problem 12.2

1. 

version 1: the case in this version means the name of the sex in that year

version 2: the case in this version means the name in that year 

version 3:  a case in version three means the name of that sex.

2. 
The chain of R commands look like below. Since version two have F and M separate, it is wider.
```{r}
VersionOne <- BabyNames %>%
  filter( name %in% c("Ida","Robert","Theresa")) %>%
  filter(year %in% c(1912,2012)) %>%
  transmute(name, sex, year, nbabies=count) %>%
  arrange(year,name)

VersionTwo <- VersionOne %>%
  pivot_wider(names_from = "sex", values_from = "nbabies") %>%
  arrange(name)

VersionTwo

```

3. 
The chain of R commands look like below. Since version three have specific year 1912 and 2012 , it is wider.
```{r}
VersionThree <- VersionOne %>%
  pivot_wider(names_from = "year", values_from = "nbabies")

VersionThree%>%
  pivot_longer(cols = c("1912","2012"), names_to = "year", values_to = "nbabies") %>%
  arrange(year,name)%>%
  na.omit
```

4. Version Two is easier to use since they use Male and female as two different variables so that it is more easier for data to be calculated.

```{r}
VersionTwo %>%
  mutate(ratio=M/F)

```

5. 
I will translate to “Version Two” before using data verbs since the ratio can't be calculated in version one since M and F is not a separate variable. We need Female and Male to be variables for us to calculate the ratio so I will translate to version two.


### Problem 12.3

1.
A versus C: A is wider,  Country expand in three variables Algeria, Brazil, Columbia in Data Frame A in two different year.

B versus C: B is wider, Year from Data Frame C derived two specific variables: Y2000, Y2001 in Data Frame B.

A versus B: I think this can not be compared. Since Data frame B expand the variable year into Y2000 and Y2001. However, Data frame A expand the variable country into three different country. In this case, we can't compare which one is wider.


2.I think Data Frame B is easier for us to calculate the change from 2000 to 2001. It can be done by mutate() function. Mutate(Change=Y2001-Y2000). From this function, we can easily see the change between two country. 


3.I think Data Frame C is easiest to work with. We create a new variable called Continent to the table. We can use function summarise() and sum()to find the sum.
We can find the sum of the values from the code below:

DataFrameCNew %>% 
group_by(Continent)%>% 
summarise(count=sum(Value))



