---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 17"
author: Xiaoying Wang
output: html_notebook
---

## Assigned Exercises

- DC Chapter 17 Exercises: 17.1 (part 1 & 3), 17.4 (part 1 & 2),  17.5


## Front Matter

```{r}

# all packages used for the assignment
library(dcData)
library(tidyverse)
library(mosaic)
library(ggplot2)

```

### Problem 17.1
part 1
```{r}
BoyName <-
BabyNames %>%
filter(sex == 'M'& grepl("[aeiou]$",name, ignore.case = TRUE)) %>%
group_by(name) %>%
summarise(total = sum(count)) %>%
arrange(desc(total)) %>%
top_n(10)

BoyName
```
part 3
```{r}
Name_endinJoes <-
BabyNames %>%
filter(str_detect(name, "joe$")) %>%
group_by(name) %>%
summarise(total = sum(count)) %>%
arrange(desc(total)) %>%
top_n(10)

Name_endinJoes
```

### Problem 17.4
part 1: The length that match the pattern will be 2.

Part2: There are 61 different string will match




### Problem 17.5

1. The name that have bar like: Barbara, Barry, and Bart
```{r}
BibleNames <- 
  readr::read_csv("https://mdbeckman.github.io/dcSupplement/data/BibleNames.csv")
NameList <- 
  BabyNames %>% 
  group_by(name, sex) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) 

NameList %>%
  filter(grepl("bar", name, ignore.case = TRUE))

```
2.The name that have dam like: Adam, Damian, Damon
```{r}
NameList <- 
  BabyNames %>% 
  group_by(name, sex) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) 

NameList%>%
  filter(grepl("dam", name, ignore.case = TRUE))
  
```

3.The name that have lory like: Mallory, Glory, Lory
```{r}
NameList <- 
  BabyNames %>% 
  group_by(name, sex) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) 

NameList%>%
  filter(grepl("lory", name, ignore.case = TRUE))
```
1. Name end with Bar like: Ambar, Jabbar, Akbar
```{r}
NameList <- 
  BabyNames %>% 
  group_by(name, sex) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) 


NameList %>%
  filter( grepl( "bar$", name ) ) 
```

2. Name end with dam like: Adam, Addam, and Saddam
```{r}
NameList <- 
  BabyNames %>% 
  group_by(name, sex) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) 


NameList %>%
  filter( grepl( "dam$", name ) ) 
```
3. Name end with lory like: Mallory, Glory, Malory
```{r}
NameList <- 
  BabyNames %>% 
  group_by(name, sex) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) 


NameList %>%
  filter( grepl( "lory$", name ) ) 
```

