---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 13 & 16"
author: Xiaoying Wang
output: html_notebook
---

## Assigned Exercises

- DC Chapter 13 & 16 Exercises: 13.1, 13.2, 16.1, 16.2


## Front Matter

```{r}

# all packages used for the assignment
library(dcData)
library(tidyverse)
library(mosaic)
library(ggplot2)
library(lubridate)
```

### Problem 13.1
```{r}
Babynames %>% 
  group_by(name) %>%
  filter(sex=="F") %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) %>%
  head(5)
  
```
```{r}
Babynames %>% 
  group_by(name) %>%
  filter(sex=="M") %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) %>%
  head(5)
  
```

### Problem 13.2
1. 
```{r}
TOP100popularname<-Babynames%>%
  group_by(year, name)%>%
  summarise(total=sum(count))

Rankings <- TOP100popularname %>%
  group_by(year) %>%
  mutate(ranking=ifelse((rank(desc(total))) <= 100,"Top_100", "Below"))

Rankings <- Rankings %>%
  group_by(year,ranking) %>%
  summarise(total=sum(total)) %>%
  arrange(desc(year))

Rankings
```

2.
```{r}
Rankingswide <- Rankings %>%
  pivot_wider(names_from = ranking,values_from = total)%>%
  mutate(fraction100=Top_100/(Below + Top_100))

Rankingswide
```

3.

```{r}
ggplot(Rankingswide)+
  aes(x=year,y=fraction100) +
  geom_line(size=0.5)+
  theme_bw()%>%
  labs(title='Fraction Changed Over the Years')
```





### Problem 16.1

1. 

```{r}
Gauss <- mdy("April 30, 1777")
Xiaoying <- mdy("April 12, 2002")
Xiaoying-Gauss
```

2. 
```{r}
Turing <- mdy("06-23-1912")
Xiaoying - Turing
```


3.
```{r}
Bell<- dmy("3 MArch 1874")
Xiaoying -  Bell
```

4.
```{r}
ww1= mdy_hm("Nov. 11th, 1918 at 11:00 am")
Xiaoying<- mdy_hm("April. 12th, 2002 at 5:00am")
Xiaoying - ww1
```

5.
```{r}
Moonlanding = mdy("July 20, 1969")
Xiaoying <- mdy("April 12, 2002")
Xiaoying - Moonlanding

```

### Problem 16.2

“42,659.30”
as.numeric()

“17%”
readr::parse_number()

“Nineteen”
Neither of the two are able to convert numbers

“£100”
readr::parse_number()

“9.8 m/seconds-square”
readr::parse_number()

“9.8 m/s^2”
readr::parse_number()

“6.62606957 × 10^-34 m2 kg / s”
Neither of the two are able to convert numbers

“6.62606957e-34”
Both are able to convert this string to numeric

“42.659,30” (A European style)
Neither of the two are able to convert numbers
