---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 7"
author: Xiaoying Wang
output: html_notebook
---

## Assigned Exercises

- DC Chapter 7 Exercises: 7.3/7.5/7.6/7.7/7.8

## Front Matter

```{r}

# all packages used for the assignment
library(dcData)
library(tidyverse)
library(mosaic)
```

### Problem 7.3
1. There are 80101 cases in the cases
2. Top five is BESTY HODGES(14399), DON SAMUELS(14170),MARK ANDREW(12757),undervote(10598), JACKIE CHERRYHOMES(6470)
3. There are 834 ballots in First choice selections
There are 10598 ballots in Second choice selections
There are 19210 ballots in Third choice selections
4. 
5. P-06 had the highest number(9711)of ballots cast
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(votes = n()) %>%
  arrange(desc(votes))

```
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  filter(First=="undervote") %>%
  nrow()

```
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  filter(Second=="undervote") %>%
  nrow()
```
```{r}
Minneapolis2013 %>%
  group_by(Third) %>%
  filter(Third=="undervote") %>%
  nrow()
```

```{r}
Minneapolis2013 %>%
  group_by(First,Second) %>%
  summarise(votes = n()) %>%
  arrange(desc(votes))
```



```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(votes = n()) %>%
  arrange(desc(votes))
```
### Problem 7.6
```{r}
library(esquisse)
library(dplyr)
library(ggplot2)

ZipGeography %>%
 filter(!(Timezone %in% " ") | is.na(Timezone)) %>%
 ggplot() +
 aes(x = LandArea, y = Population, colour = State) +
 geom_point(shape = "circle", 
 size = 1.5) +
 scale_color_hue(direction = 1) +
 theme_minimal()
```

#Problem 7.7
```{r}
  Patients %>%
  group_by(sex) %>%
  summarise(count = n(), meanAge = mean(age))
```

a. The variable appear in output that group the patients by sex and the mean age in category of sex

#Problem 7.8
1. There is a positive relationship between Foreignborn in a zip code and the number who speakalanguageotherthanEnglishathome5yearsandover. Higher Foriegnborn in a zip code, the higher number who speak a language other than English at home 5 years and over 
```{r} 
library(esquisse)
library(ggplot2)

ggplot(ZipDemography) +
 aes(x = Foreignborn, y = SpeakalanguageotherthanEnglishathome5yearsandover) +
 geom_point(shape = "circle", size = 1.5, colour = "#112446") +
 theme_minimal()

```
